---
title: "Project"
author: "Benjamin Huang"
date: "2024-03-31"
output: pdf_document
---

#Part 1 Convolutions
##In this part, you will see the effect of adding two distributions together. Simulate ğ‘‹1, ğ‘‹2, and then 
##compute their sum ğ‘Œ = ğ‘‹1 + ğ‘‹2. Classify Y as an (a, b, 0) distribution and give its parameters. 
```{r Geometric dist}
set.seed(461)
x1 <- rgeom(10000, 1/(1+12))
x2 <- rgeom(10000, 1/(1+12))
y <- x1 + x2
(table <- table(y))

par(mfrow = c(1,3))
hist(x1)
hist(x2)
hist(y)

p <- numeric(60)
for (i in 1:60) {
  p[i] <- (i+1)*table[i+1]/table[i]
}
p
x <- 2:61
lm(p[1:60]~x)

par(mfrow = c(1, 2))
hist(y, breaks = 15)
hist(rnbinom(10000, 2, 1/(1+12)), breaks = 15)
```

```{r Binomial dist}
set.seed(461)
x1 <- rbinom(10000, 24, 0.6)
x2 <- rbinom(10000, 36, 0.6)
y <- x1 + x2
(table <- table(y))

par(mfrow = c(1,3))
hist(x1)
hist(x2)
hist(y)

p <- numeric(24)
for (i in 1:24) {
  p[i] <- (i+22)*table[i+1]/table[i]
}
p
x <- 26:46
lm(p[4:24]~x)

par(mfrow = c(1, 2))
hist(y, breaks = 15)
hist(rbinom(10000, 62, 0.583), breaks = 15)
```

```{r Poisson dist}
set.seed(461)
x1 <- rpois(10000, 16)
x2 <- rpois(10000, 20)
y <- x1 + x2
(table <- table(y))

par(mfrow = c(1,3))
hist(x1)
hist(x2)
hist(y)

p <- numeric(40)
for (i in 1:40) {
  p[i] <- (i+17)*table[i+2]/table[i+1]
}
p
x <- 21:52
lm(p[4:35]~x)

par(mfrow = c(1, 2))
hist(y, breaks = 15)
hist(rpois(10000, 35), breaks = 10)
```

#Part 2 Compound Distributions
##In this part, you will create a collective risk model with N being the number of claims and ğ‘‹ğ‘– being the amount of loss. Simulate ğ‘, ğ‘‹ğ‘–, and the sum ğ‘† = ğ‘‹1 + ğ‘‹2 + â‹¯ + ğ‘‹ğ‘. Compute ğ¸[ğ‘†], ğ‘‰ğ‘ğ‘Ÿ[ğ‘†], and compare to the theoretical values using the law of total expectation. 
```{r Poisson & Exponential}
set.seed(461)
n <- rpois(10000, 25)
x_i <- rexp(10000, 1/100)

mean_n <- mean(n)
var_n <- var(n)
mean_x_i <- mean(x_i)
var_x_i <- var(x_i)

mean_s <- mean_n * mean_x_i
var_s <- mean_n * var_x_i + var_n * mean_x_i^2
cat("mean of aggregate loss:", mean_s, "\n")
cat("variance of aggregate loss:", var_s)
```
$$
\begin{align*}

& N \sim Poi(\lambda = 25), \: X \sim Exp(\theta = 100)
\\
& E(N) = \lambda = 25, \: Var(N) = \lambda = 25
\\
& E(X) = \theta^{1} \times 1! = 100, \: E(X^{2}) = \theta^{2} \times 2! = 20000, \: Var(X) = 10000
\\
& \therefore E(S) = E(N) \times E(X) = 2500, \: Var(S) = E(N) \times Var(X) + Var(N) \times E(X)^{2} = 500000

\end{align*}
$$
```{r Poisson & Lognormal}
set.seed(461)
n <- rpois(10000, 100)
x_i <- rlnorm(10000, meanlog = 1, sdlog = 2)

mean_n <- mean(n)
var_n <- var(n)
mean_x_i <- mean(x_i)
var_x_i <- var(x_i)

mean_s <- mean_n * mean_x_i
var_s <- mean_n * var_x_i + var_n * mean_x_i^2
cat("mean of aggregate loss:", mean_s, "\n")
cat("variance of aggregate loss:", var_s)
```
$$
\begin{align*}

& N \sim Poi(\lambda = 100), \: X \sim Lognormal(\mu = 1, \sigma = 2)
\\
& E(N) = \lambda = 100, \: Var(N) = \lambda = 100
\\
& E(X) = exp(\mu + \frac{1}{2}\sigma^{2}) \approx 20.09, \: E(X^{2}) = exp(2\mu + 2\sigma^{2}) \approx 22026.47, \: Var(X) \approx 21622.86
\\
& \therefore E(S) = E(N) \times E(X) = 2009, \: Var(S) = E(N) \times Var(X) + Var(N) \times E(X)^{2} = 2202646.81

\end{align*}
$$

```{r Binomial & Gamma}
set.seed(461)
n <- rbinom(10000, 36, 0.6)
x_i <- rgamma(10000, shape = 100, rate = 1/2)

mean_n <- mean(n)
var_n <- var(n)
mean_x_i <- mean(x_i)
var_x_i <- var(x_i)

mean_s <- mean_n * mean_x_i
var_s <- mean_n * var_x_i + var_n * mean_x_i^2
cat("mean of aggregate loss:", mean_s, "\n")
cat("variance of aggregate loss:", var_s)
```
$$
\begin{align*}

& N \sim Bin(m = 36, q = 0.6), \: X \sim Gamma(\alpha = 100, \theta = 2)
\\
& E(N) = mq = 21.6, \: Var(N) = mq(1-q) = 8.64
\\
& E(X) = \theta^{1}(\alpha + 1 - 1) = 200, \: E(X^{2}) = \theta^{2}(\alpha + 2 - 1)(\alpha + 1 -1) = 40400, \: Var(X) = 400
\\
& \therefore E(S) = E(N) \times E(X) = 4320, \: Var(S) = E(N) \times Var(X) + Var(N) \times E(X)^{2} = 354240

\end{align*}
$$

#Part 3 Credibility Theory
#For each of the three models in Part 2, determine the credibility standards with
$$
\begin{align*}

& For \: r = 0.99, p = 0.9, \: E(S) = 2500, \: Var(S) = 500000
\\
& \mathbb{P}\{ -r\xi \leq \bar{X} - \xi \leq r\xi \} \geq p, \: \mathbb{P}(|\frac{\bar{X}-\xi}{\sigma/\sqrt{n}}| \leq \frac{r\xi\sqrt{n}}{\sigma}) \geq p
\\
& \Rightarrow \mathbb{P}(|\frac{\bar{X}-E(X)}{Var(\bar{X})}| \leq \frac{rE(X)}{Var(\bar{X})}=y_{p}) \geq p
\\
& Let \: X = S(Aggregate \: Loss)
\\
& \Rightarrow \frac{rE(X)}{Var(\bar{X})} = \frac{0.99 \times 2500}{500000/10000} = 49.5 \geq y_{0.95} = 1.645

\end{align*}
$$

$$
\begin{align*}

& For \: r = 0.95, p = 0.95, \: E(S) = 2009, \: Var(S) = 2202646.81
\\
& \mathbb{P}\{ -r\xi \leq \bar{X} - \xi \leq r\xi \} \geq p, \: \mathbb{P}(|\frac{\bar{X}-\xi}{\sigma/\sqrt{n}}| \leq \frac{r\xi\sqrt{n}}{\sigma}) \geq p
\\
& \Rightarrow \mathbb{P}(|\frac{\bar{X}-E(X)}{Var(\bar{X})}| \leq \frac{rE(X)}{Var(\bar{X})}=y_{p}) \geq p
\\
& Let \: X = S(Aggregate \: Loss)
\\
& \Rightarrow \frac{rE(X)}{Var(\bar{X})} = \frac{0.95 \times 2009}{2202646.81/10000} \approx 8.66 \geq y_{0.975} = 1.96

\end{align*}
$$

$$
\begin{align*}

& For \: r = 0.90, p = 0.99, \: E(S) = 4320, \: Var(S) = 354240
\\
& \mathbb{P}\{ -r\xi \leq \bar{X} - \xi \leq r\xi \} \geq p, \: \mathbb{P}(|\frac{\bar{X}-\xi}{\sigma/\sqrt{n}}| \leq \frac{r\xi\sqrt{n}}{\sigma}) \geq p
\\
& \Rightarrow \mathbb{P}(|\frac{\bar{X}-E(X)}{Var(\bar{X})}| \leq \frac{rE(X)}{Var(\bar{X})}=y_{p}) \geq p
\\
& Let \: X = S(Aggregate \: Loss)
\\
& \Rightarrow \frac{rE(X)}{Var(\bar{X})} = \frac{0.9 \times 4320}{354240/10000} \approx 109.76 \geq y_{0.995} = 2.575

\end{align*}
$$