---
title: "Project"
author: "Benjamin Huang"
date: "2024-03-31"
output: pdf_document
---

#Part 1 Convolutions
##In this part, you will see the effect of adding two distributions together. Simulate ğ‘‹1, ğ‘‹2, and then 
##compute their sum ğ‘Œ = ğ‘‹1 + ğ‘‹2. Classify Y as an (a, b, 0) distribution and give its parameters. 
```{r Geometric dist}
set.seed(461)
x1 <- rgeom(10000, 1/(1+12))
x2 <- rgeom(10000, 1/(1+12))
y <- x1 + x2
(table <- table(y))

par(mfrow = c(1,3))
hist(x1)
hist(x2)
hist(y)

p <- numeric(60)
for (i in 1:60) {
  p[i] <- (i+1)*table[i+1]/table[i]
}
p
x <- 2:61
lm(p[1:60]~x)

par(mfrow = c(1, 2))
hist(y, breaks = 15)
hist(rnbinom(10000, 2, 1/(1+12)), breaks = 15)
```

```{r Binomial dist}
set.seed(461)
x1 <- rbinom(10000, 24, 0.6)
x2 <- rbinom(10000, 36, 0.6)
y <- x1 + x2
(table <- table(y))

par(mfrow = c(1,3))
hist(x1)
hist(x2)
hist(y)

p <- numeric(24)
for (i in 1:24) {
  p[i] <- (i+22)*table[i+1]/table[i]
}
p
x <- 26:46
lm(p[4:24]~x)

par(mfrow = c(1, 2))
hist(y, breaks = 15)
hist(rbinom(10000, 62, 0.583), breaks = 15)
```

```{r Poisson dist}
set.seed(461)
x1 <- rpois(10000, 16)
x2 <- rpois(10000, 20)
y <- x1 + x2
(table <- table(y))

par(mfrow = c(1,3))
hist(x1)
hist(x2)
hist(y)

p <- numeric(40)
for (i in 1:40) {
  p[i] <- (i+17)*table[i+2]/table[i+1]
}
p
x <- 21:52
lm(p[4:35]~x)

par(mfrow = c(1, 2))
hist(y, breaks = 15)
hist(rpois(10000, 35), breaks = 10)
```

#Part 2 Compound Distributions
##In this part, you will create a collective risk model with N being the number of claims and ğ‘‹ğ‘– being the amount of loss. Simulate ğ‘, ğ‘‹ğ‘–, and the sum ğ‘† = ğ‘‹1 + ğ‘‹2 + â‹¯ + ğ‘‹ğ‘. Compute ğ¸[ğ‘†], ğ‘‰ğ‘ğ‘Ÿ[ğ‘†], and compare to the theoretical values using the law of total expectation. 
```{r Poisson & Exponential}
set.seed(461)
n <- rpois(10000, 25)
x_i <- rexp(10000, 1/100)

mean_n <- mean(n)
var_n <- var(n)
mean_x_i <- mean(x_i)
var_x_i <- var(x_i)

mean_s <- mean_n * mean_x_i
var_s <- mean_n * var_x_i + var_n * mean_x_i^2
cat("mean of aggregate loss:", mean_s, "\n")
cat("variance of aggregate loss:", var_s)
```

