---
title: "Project"
author: "Benjamin Huang, Sueking Leung"
date: "2024-03-31"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

#Part 1 Convolutions
##In this part, you will see the effect of adding two distributions together. Simulate ğ‘‹1, ğ‘‹2, and then compute their sum ğ‘Œ = ğ‘‹1 + ğ‘‹2. Classify Y as an (a, b, 0) distribution and give its parameters. 
```{r Geometric dist}
sample_size <- 10000
beta1 <- 12
beta2 <- 12

set.seed(461)
x1 <- rgeom(sample_size, 1/(1+beta1)) # Geometric distribution with beta = 12
x2 <- rgeom(sample_size, 1/(1+beta2))
y <- x1 + x2
(table <- table(y))

par(mfrow = c(1,3))
hist(x1)
hist(x2)
hist(y)

p <- numeric(60)
for (i in 1:60) {
  p[i] <- (i+1)*table[i+1]/table[i]
}
p
x <- 2:61
lm(p[1:60]~x) # pick samples that are large enough

# We get a = .93, b = 1, since a > 0, we determine y follows a Negative Binomial distribution.
# Through NB distribution's formulas, we get r = 2, beta = 12.

par(mfrow = c(1, 2))
hist(y, breaks = 15)
hist(rnbinom(sample_size, 2, 1/(1+12)), breaks = 15)
```

```{r Binomial dist}
sample_size <- 10000
trial1 <- 24
trial2 <- 36
success1 <- 0.6
success2 <- 0.6
set.seed(461)

x1 <- rbinom(sample_size, trial1, success1) # Binomial distribution with m = 24, q = 0.6
x2 <- rbinom(sample_size, trial2, success2) # Binomial distribution with m = 36, q = 0.6
y <- x1 + x2
(table <- table(y))

par(mfrow = c(1,3))
hist(x1)
hist(x2)
hist(y)

p <- numeric(24)
for (i in 1:24) {
  p[i] <- (i+22)*table[i+1]/table[i]
}
p
x <- 26:46
lm(p[4:24]~x) # pick samples that are large enough

# We get a = -1.4, b = 88.3, since a < 0, we determine y follows a Binomial distribution.
# Through Binomial distribution's formulas, we get m = 62, q = 0.583.

par(mfrow = c(1, 2))
hist(y, breaks = 15)
hist(rbinom(sample_size, 62, 0.583), breaks = 15)
```

```{r Poisson dist}
sample_size <- 10000
lambda1 <- 16
lambda2 <- 20
set.seed(461)

x1 <- rpois(sample_size, lambda1) # Poisson distribution with lambda = 16
x2 <- rpois(sample_size, lambda2) # Poisson distribution with lambda = 20
y <- x1 + x2
(table <- table(y))

par(mfrow = c(1,3))
hist(x1)
hist(x2)
hist(y)

p <- numeric(40)
for (i in 1:40) {
  p[i] <- (i+17)*table[i+2]/table[i+1]
}
p
x <- 21:52
lm(p[4:35]~x) # pick samples that are large enough

# We get a = 0.05, b = 34.6, since a is very close to 0, we determine y follows a Poisson distribution.
# Through Poisson distribution's formulas, we get lambda = 35

par(mfrow = c(1, 2))
hist(y, breaks = 15)
hist(rpois(sample_size, 35), breaks = 10)
```

#Part 2 Compound Distributions
##In this part, you will create a collective risk model with N being the number of claims and ğ‘‹ğ‘– being the amount of loss. Simulate ğ‘, ğ‘‹ğ‘–, and the sum ğ‘† = ğ‘‹1 + ğ‘‹2 + â‹¯ + ğ‘‹ğ‘. Compute ğ¸[ğ‘†], ğ‘‰ğ‘ğ‘Ÿ[ğ‘†], and compare to the theoretical values using the law of total expectation. 
```{r Poisson & Exponential_method1}
sample_size <- 10000
lambda <- 25
theta <- 100
set.seed(441)

n1 <- rpois(sample_size, lambda) # create the distribution for number of claims first
s1 <- numeric(sample_size) # create a vector for the sum
for (i in 1:sample_size) {
  x_i <- rexp(n1[i], 1/theta) # create x_i for the ith number of claims
  s1[i] <- sum(x_i)
}

mean_s1 <- mean(s1)
var_s1 <- var(s1)
cat("mean of aggregate loss by S1:", mean_s1, "\n")
cat("variance of aggregate loss by S1:", var_s1, "\n")
```
```{r Poisson & Exponential_method2}
sample_size <- 10000
lambda <- 25
theta <- 100
set.seed(441)

s2 <- numeric(sample_size) # create a vector for the sum
for(k in 1:sample_size){
  n2 <- rpois(1, lambda) # create the distribution for number of claims inside the loop
  x2 <- rexp(n2, 1/theta) # create  n2 x2
  s2[k] <- sum(x2)
}

mean_s2 <- mean(s2)
var_s2 <- var(s2)
cat("mean of aggregate loss by S2:", mean_s2, "\n")
cat("variance of aggregate loss by S2:", var_s2)
```

$$
\begin{align*}

& N \sim Poi(\lambda = 25), \: X \sim Exp(\theta = 100)
\\
& E(N) = \lambda = 25, \: Var(N) = \lambda = 25
\\
& E(X) = \theta^{1} \times 1! = 100, \: E(X^{2}) = \theta^{2} \times 2! = 20000, \: Var(X) = 10000
\\
& \therefore E(S) = E(N) \times E(X) = 2500, \: Var(S) = E(N) \times Var(X) + Var(N) \times E(X)^{2} = 500000

\end{align*}
$$
```{r Poisson & Lognormal_method1}
sample_size <- 10000
lambda <- 100
mu <- 1
sigma <- 2
set.seed(441)

n1 <- rpois(sample_size, lambda) # create the distribution for number of claims first
s1 <- numeric(sample_size) # create a vector for the sum
for (i in 1:sample_size) {
  x_i <- rlnorm(n1[i], meanlog = mu, sdlog = sigma) # create x_i for the ith number of claims
  s1[i] <- sum(x_i)
}


mean_s1 <- mean(s1)
var_s1 <- var(s1)
cat("mean of aggregate loss by S1:", mean_s1, "\n")
cat("variance of aggregate loss by S1:", var_s1, "\n")

```

```{r Poisson & Lognormal_method2}
sample_size <- 10000
lambda <- 100
mu <- 1
sigma <- 2
set.seed(441)

s2 <- numeric(sample_size) # create a vector for the sum
for (k in 1:sample_size) {
  n2 <- rpois(1, lambda) # create the distribution for number of claims inside the loop
  x2 <- rlnorm(n2, mu, sigma) # create  n2 x2
  s2[k] <- sum(x2)
}

mean_s2 <- mean(s2)
var_s2 <- var(s2)
cat("mean of aggregate loss by S2:", mean_s2, "\n")
cat("variance of aggregate loss by S2:", var_s2)
```

$$
\begin{align*}

& N \sim Poi(\lambda = 100), \: X \sim Lognormal(\mu = 1, \sigma = 2)
\\
& E(N) = \lambda = 100, \: Var(N) = \lambda = 100
\\
& E(X) = exp(\mu + \frac{1}{2}\sigma^{2}) \approx 20.09, \: E(X^{2}) = exp(2\mu + 2\sigma^{2}) \approx 22026.47, \: Var(X) \approx 21622.86
\\
& \therefore E(S) = E(N) \times E(X) = 2009, \: Var(S) = E(N) \times Var(X) + Var(N) \times E(X)^{2} = 2202646.81

\end{align*}
$$

```{r Binomial & Gamma_method1}
sample_size <- 10000
trial <- 36
success <- 0.6
alpha <- 100
beta <- 2
set.seed(441)

n1 <- rbinom(sample_size, trial, success) # create the distribution for number of claims first
s1 <- numeric(sample_size) # create a vector for the sum
for (i in 1:sample_size) {
  x_i <- rgamma(n1[i], shape = alpha, rate = 1/beta) # create x_i for the ith number of claims
  s1[i] <- sum(x_i)
}

mean_s1 <- mean(s1)
var_s1 <- var(s1)
cat("mean of aggregate loss by S1:", mean_s1, "\n")
cat("variance of aggregate loss by S1:", var_s1, "\n")
```

```{r Binomial & Gamma_method2}
sample_size <- 10000
trial <- 36
success <- 0.6
alpha <- 100
beta <- 2
set.seed(441)

s2 <- numeric(sample_size) # create a vector for the sum
for (k in 1:sample_size) {
  n2 <- rbinom(1, trial, success) # create the distribution for number of claims inside the loop
  x2 <- rgamma(n2, shape = alpha, rate = 1/beta) # create  n2 x2
  s2[k] <- sum(x2)
}

mean_s2 <- mean(s2)
var_s2 <- var(s2)
cat("mean of aggregate loss by S2:", mean_s2, "\n")
cat("variance of aggregate loss by S2:", var_s2)
```

$$
\begin{align*}

& N \sim Bin(m = 36, q = 0.6), \: X \sim Gamma(\alpha = 100, \theta = 2)
\\
& E(N) = mq = 21.6, \: Var(N) = mq(1-q) = 8.64
\\
& E(X) = \theta^{1}(\alpha + 1 - 1) = 200, \: E(X^{2}) = \theta^{2}(\alpha + 2 - 1)(\alpha + 1 -1) = 40400, \: Var(X) = 400
\\
& \therefore E(S) = E(N) \times E(X) = 4320, \: Var(S) = E(N) \times Var(X) + Var(N) \times E(X)^{2} = 354240

\end{align*}
$$

#Part 3 Credibility Theory
#For each of the three models in Part 2, determine the credibility standards with
$$
\begin{align*}

& For \: r = 0.01, p = 0.9,
\\
& N = Poi(\lambda = 25), \: X_{i} = Exp(\theta = 100 ): \: E(S) = 2500, \: Var(S) = 500000
\\
& N = Poi(\lambda = 100), \: X_{i} = LogNormal(\mu = 1, \sigma = 2 ): \: E(S) = 2009, \: Var(S) = 2202646.81
\\
& N = Bin(m = 36, q = 0.6), \: X_{i} = Gamma(\alpha = 100, \theta = 2 ): \: E(S) = 4320, \: Var(S) = 354240
\\
& \mathbb{P}\{ -r\xi \leq \bar{X} - \xi \leq r\xi \} \geq p, \: \mathbb{P}(|\frac{\bar{X}-\xi}{\sigma/\sqrt{n}}| \leq \frac{r\xi\sqrt{n}}{\sigma}) \geq p
\\
& \Rightarrow \mathbb{P}(|\frac{\bar{X}-E(X)}{\sqrt{Var(\bar{X})}}| \leq \frac{rE(X)}{\sqrt{Var(\bar{X})}}=y_{p}) \geq p
\\
& Let \: X = S(Aggregate \: Loss)
\\
& For \: N = Poi(\lambda = 25), \: X_{i} = Exp(\theta = 100 ):
\\
& \frac{rE(X)}{\sqrt{Var(\bar{X})}} = \frac{0.01 \times 2500}{\sqrt{500000/10000}} \approx 3.536 \geq y_{0.95} = 1.645
\\
\\
& For \: N = Poi(\lambda = 100), \: X_{i} = LogNormal(\mu = 1, \sigma = 2 ):
\\
& \frac{rE(X)}{\sqrt{Var(\bar{X})}} = \frac{0.01 \times 2009}{\sqrt{2202646.81/10000}} \approx 1.354 \leq y_{0.95} = 1.645
\\
\\
& For \: N = Bin(m = 36, q = 0.6), \: X_{i} = Gamma(\alpha = 100, \theta = 2 ):
\\
& \frac{rE(X)}{\sqrt{Var(\bar{X})}} = \frac{0.01 \times 4320}{\sqrt{354240/10000}} \approx 7.258 \geq y_{0.95} = 1.645

\end{align*}
$$

$$
\begin{align*}

& For \: r = 0.05, p = 0.95,
\\
& N = Poi(\lambda = 25), \: X_{i} = Exp(\theta = 100 ): \: E(S) = 2500, \: Var(S) = 500000
\\
& N = Poi(\lambda = 100), \: X_{i} = LogNormal(\mu = 1, \sigma = 2 ): \: E(S) = 2009, \: Var(S) = 2202646.81
\\
& N = Bin(m = 36, q = 0.6), \: X_{i} = Gamma(\alpha = 100, \theta = 2 ): \: E(S) = 4320, \: Var(S) = 354240
\\
& \mathbb{P}\{ -r\xi \leq \bar{X} - \xi \leq r\xi \} \geq p, \: \mathbb{P}(|\frac{\bar{X}-\xi}{\sigma/\sqrt{n}}| \leq \frac{r\xi\sqrt{n}}{\sigma}) \geq p
\\
& \Rightarrow \mathbb{P}(|\frac{\bar{X}-E(X)}{\sqrt{Var(\bar{X})}}| \leq \frac{rE(X)}{\sqrt{Var(\bar{X})}}=y_{p}) \geq p
\\
& Let \: X = S(Aggregate \: Loss)
\\
& For \: N = Poi(\lambda = 25), \: X_{i} = Exp(\theta = 100 ):
\\
& \frac{rE(X)}{\sqrt{Var(\bar{X})}} = \frac{0.05 \times 2500}{\sqrt{500000/10000}} \approx 17.678 \geq y_{0.975} = 1.96
\\
\\
& For \: N = Poi(\lambda = 100), \: X_{i} = LogNormal(\mu = 1, \sigma = 2 ):
\\
& \frac{rE(X)}{\sqrt{Var(\bar{X})}} = \frac{0.05 \times 2009}{\sqrt{2202646.81/10000}} \approx 6.768 \geq y_{0.975} = 1.96
\\
\\
& For \: N = Bin(m = 36, q = 0.6), \: X_{i} = Gamma(\alpha = 100, \theta = 2 ):
\\
& \frac{rE(X)}{\sqrt{Var(\bar{X})}} = \frac{0.05 \times 4320}{\sqrt{354240/10000}} \approx 36.292 \geq y_{0.975} = 1.96

\end{align*}
$$

$$
\begin{align*}

& For \: r = 0.10, p = 0.99,
\\
& N = Poi(\lambda = 25), \: X_{i} = Exp(\theta = 100 ): \: E(S) = 2500, \: Var(S) = 500000
\\
& N = Poi(\lambda = 100), \: X_{i} = LogNormal(\mu = 1, \sigma = 2 ): \: E(S) = 2009, \: Var(S) = 2202646.81
\\
& N = Bin(m = 36, q = 0.6), \: X_{i} = Gamma(\alpha = 100, \theta = 2 ): \: E(S) = 4320, \: Var(S) = 354240
\\
& \mathbb{P}\{ -r\xi \leq \bar{X} - \xi \leq r\xi \} \geq p, \: \mathbb{P}(|\frac{\bar{X}-\xi}{\sigma/\sqrt{n}}| \leq \frac{r\xi\sqrt{n}}{\sigma}) \geq p
\\
& \Rightarrow \mathbb{P}(|\frac{\bar{X}-E(X)}{\sqrt{Var(\bar{X})}}| \leq \frac{rE(X)}{\sqrt{Var(\bar{X})}}=y_{p}) \geq p
\\
& Let \: X = S(Aggregate \: Loss)
\\
& For \: N = Poi(\lambda = 25), \: X_{i} = Exp(\theta = 100 ):
\\
& \frac{rE(X)}{\sqrt{Var(\bar{X})}} = \frac{0.1 \times 2500}{\sqrt{500000/10000}} \approx 35.355 \geq y_{0.995} = 2.575
\\
\\
& For \: N = Poi(\lambda = 100), \: X_{i} = LogNormal(\mu = 1, \sigma = 2 ):
\\
& \frac{rE(X)}{\sqrt{Var(\bar{X})}} = \frac{0.1 \times 2009}{\sqrt{2202646.81/10000}} \approx 13.537 \geq y_{0.995} = 2.575
\\
\\
& For \: N = Bin(m = 36, q = 0.6), \: X_{i} = Gamma(\alpha = 100, \theta = 2 ):
\\
& \frac{rE(X)}{\sqrt{Var(\bar{X})}} = \frac{0.1 \times 4320}{\sqrt{354240/10000}} \approx 72.583 \geq y_{0.995} = 2.575

\end{align*}
$$